The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-07 Paper/Paper.tex
Further work in proving that colim commute with product

Next we need to define the introduction rules for the paths.
Let us start by making maps $I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \> B_i \> f)  \rightarrow \hocolim \> F \> f$.

@@

>>>>

Next we need to define the introduction rules for the paths.
Let us start by making maps $I^1 \times B_i \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$.
Since homotopy colimits commute with polynomials, it suffices to make a map $\hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f)  \rightarrow \hocolim \> F \> f$.

@@

\begin{proof}
This is the most difficult one, because colimits only commute with products if there are exponentials.
\end{proof}
